### 2021-03-09 text/draft.tex
clean up text & docu

!! Say something to the effect that all data and code are available on
GitHub.

!! In this chapter, the prototype for a machine indexing of Edoc is
presented. The focus is primarily on practical implementation although
care is taken to spell out design decisions in as much detail as is
needed.

Let us start by stating the aim of the prototype. From a functional
perspective, the prototype takes a subset of the data from Edoc as input
and provides index terms for each item in this subset as output. In
order to fulfill this aim we can distinguish a number of steps that need
to be taken:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Understand the Edoc data.\\
\item
  Select and construct a sample data set.
\item
  Use Annif to index the items in the sample data set.
\item
  Construct a gold standard from the keywords.
\item
  Assess the quality of the output based on the gold standard.
\end{enumerate}

In the sections below, these steps will be discussed in detail.

@@

\begin{itemize}
\tightlist
\item
  fulltext support
\item
  mesh; A gold standard is usually the product of manual indexing by
  ``information experts, subject experts, or potential or real end
  users'' (Golub et al. 2016, 10). This entails its own host of
  epistemic problems relating to objectivity and consistency of the
  assigned subject terms. Most importantly, however, the construction of
  a gold standard from scratch is very expensive. It is therefore not an
  option for the project at hand. Rather, I will construct what could be
  called derivative gold standards by reusing indexing data that is
  already available. Here we can distinguish two distinct kinds of
  derivative gold standards: first, I will construct a derivative gold
  standard based on the author keywords available in the sample data
  set; call this the ``derivative'' gold standard. Second, I will
  construct a derivative gold standard based on indexing metadata
  available in repositories distinct from Edoc; call this the
  ``foreign'' gold standard. -We enrich the sample items with MeSH
  keywords from PubMed if available (item needs a PubMed ID and items
  needs to be indexed with MeSH on PubMed, 1653 items match this
  requirement); the resulting file is indexed\_master\_mesh.json. Like
  so: Data.enrich\_with\_mesh(DIR + ``/indexed/indexed\_master.json,''
  DIR + ``/indexed/indexed\_master\_mesh'')
\end{itemize}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  mesh
\item
  full text
\item
  german vocabulary
\item
  select domain specific vocabularies with bartoc suggest
\end{enumerate}

@@

As mentioned in \protect\hyperlink{introduction}{section
``Introduction''}, all files, data, and code used in this project is
available at https://github.com/MHindermann/mas.

>>>>

The proof of the pudding is in the creation of a software prototype. The
prototype must take a subset of the data from Edoc as input and provide
index terms for each item in this subset as output. In order to fulfill
this aim we can distinguish five steps corresponding to sections 2 to 6
below:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Understand the Edoc data.
\item
  Select and construct an Edoc sample data set.
\item
  Use Annif to index the items in the Edoc sample data set.
\item
  Construct a gold standard from the keywords.
\item
  Assess the quality of the output based on the gold standard.
\end{enumerate}

The focus of this project lies primarily on practical implementation of
the prototype although care is taken to spell out design decisions in as
much detail as is needed.

@@

Answer some questions asked in the proposal. Briefly summarize results.
Recommend using Out of the box annif for production. sketch
implementation strategy.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  mesh. mesh; A gold standard is usually the product of manual indexing
  by ``information experts, subject experts, or potential or real end
  users'' (Golub et al. 2016, 10). This entails its own host of
  epistemic problems relating to objectivity and consistency of the
  assigned subject terms. Most importantly, however, the construction of
  a gold standard from scratch is very expensive. It is therefore not an
  option for the project at hand. Rather, I will construct what could be
  called derivative gold standards by reusing indexing data that is
  already available. Here we can distinguish two distinct kinds of
  derivative gold standards: first, I will construct a derivative gold
  standard based on the author keywords available in the sample data
  set; call this the ``derivative'' gold standard. Second, I will
  construct a derivative gold standard based on indexing metadata
  available in repositories distinct from Edoc; call this the
  ``foreign'' gold standard. / We enrich the sample items with MeSH
  keywords from PubMed if available (item needs a PubMed ID and items
  needs to be indexed with MeSH on PubMed, 1653 items match this
  requirement); the resulting file is indexed\_master\_mesh.json. Like
  so: Data.enrich\_with\_mesh(DIR + ``/indexed/indexed\_master.json,''
  DIR + ``/indexed/indexed\_master\_mesh'')
\item
  full text
\item
  german vocabulary
\item
  select domain specific vocabularies with bartoc suggest
\end{enumerate}

@@

As mentioned in \protect\hyperlink{introduction}{section
``Introduction''}, all files, data, and code used in this project is
available at https://github.com/MHindermann/mas and will not be
replicated here.
